{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-08-13 wacv_for_review.tex
Revised the section about DNN features.

\textbf{Evaluation with Deep Features} Our focus so far was to build a high
speed tracker that can run at 30fps on a single-board, embedded
system. Given this goal, we used HoG and color features in an
efficient way for the proposed {\it E}nKCF. Deep features, on
the other hand, recently have been proved to boost tracking accuracy
of the KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. For this reason, we believe that, the
{\it E}nKCF tracker can perform better with deep features trained
on ImageNet dataset. Accomodating deep features on a single-board
system prohibits from tracking at targeted speed. However, with the
availability of GPUs on the embedded system, {\it E}nKCF tracker can
afford convolutional neural network features (CNN) to improve tracking
accuracy. Therefore, we wanted to evaluate how much accuracy gain we
can achieve by switching from hand-crafted features to CNN features.

{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

  \it YoungWoo : The point of adding this section is to evaluate the
  same tracker with deep features (CNN) and see how much accuracy improvement
  we get. However, I tried to highlight that, by employing deep features
  the targeted embedded system changes from low-end (CPU-only) to 
  higher-end system (GPUs). The two papers I cited employs the features
  from the first several layers of the VGGNet. This is a common practice
  in supporting the trackers with CNN features. If I add this to figure 5,
  it does not make sense, because all the trackers we compare, use hand-crafted
  features and run on CPU. For this reason, I wanted to compare EnKCF 
  with deep features (higher-end system) and hand-crafted features (low-end system).

  The figure 7(a) and figure 5 have almost the same range (0,73 and 0.70)
  I will update the figure 5 to have 0.73 range as well. I test the EnKCF
  with CNN features only on the UAV123 dataset.
}

There has been numerous studies on applying a pretrained CNN features
to tracking-by-detection algorithms. For example, 
\cite{danelljan2015convolutional} used the activations of
the first and second convolutional layer features of the VGGNet
\cite{simonyan2014very} where their experiments showed that the first
convolutional layer features lead to slightly better precision and
success rates than the second layer. \cite{ma2015hierarchical}
proposed a KCF tracker with deeper features. Their method employs the
third convolutional layer features to get the response map. In the
next stage, they use the translation estimation from the first stage
to employ second convolutional layer features. Finally, the first
convolutional layer features is extracted from the position estimated
in the second stage. This coarse-to-fine position estimation approach
allows embedding more representative features of the object. However,
such approach requires multiple runs of a KCF at a single frame,
increasing the run-time complexity. For this reason, we follow a
similar approach to \cite{danelljan2015convolutional} to embed deep
learning features.

Our {\it E}nKCF framework provides us flexibility to exploit different
level of abstractions in different KCFs. The translation filters,
$R_{t}^{L}$ and $R_{t}^{S}$, considers more than twice larger area
than $R_{s}$. Taking this into account, we can assign deeper feature
encodings to $R_{s}$ as it requires less spatial information than
$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
the second layer features ($109\times109\times64$). This feature
assignment is represented as \textit{conv224-VGG} and shown in
fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
resolution at the first layers than than AlexNet
\cite{krizhevsky2012imagenet}.

As shown in fig.~\ref{fig:UAV123_DATASET_DeepFeatures}, both settings
of the deep features outperform the HoG and color features as proposed
in {\it E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$
in success rates (AUC). On the other hand, the \textit{conv224-VGG}
setting performs slightly better than \textit{conv222-VGG} in
precision while achieving similar success rate (AUC).  >>>>>>>

>>>>

\textbf{Evaluation with Deep Features} Our focus so far was to build a
high speed tracker that can run at 30fps on a single-board, embedded
system. Given this goal, we used HoG and color features in an
efficient way for the proposed {\it E}nKCF. Deep features, on the
other hand, recently have been used to boost tracking accuracy of the
KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. We hypothesize that the {\it E}nKCF
tracker could perform better with deep features trained on ImageNet
dataset. Utilizing pretrained deep features would not be applicable to
all the a single-board, embedded system due to their limited
computational resources. But as these days some of the single-board
systems offer GPU, we would like to see how much accuracy we can
achieve by feeding {\it E}nKCF w/ CNN features.
\begin{comment}
{\it Burak: I'm not sure what you wanted to say with ``Deep Learning
  Features.'' My edit stopped at the above paragraph because I got
  confused. At least you'll have to explain the point of adding this
  section.

@@

  YoungWoo : The point of adding this section is to evaluate the
  same tracker with deep features (CNN) and see how much accuracy improvement
  we get. However, I tried to highlight that, by employing deep features
  the targeted embedded system changes from low-end (CPU-only) to 
  higher-end system (GPUs). The two papers I cited employs the features
  from the first several layers of the VGGNet. This is a common practice
  in supporting the trackers with CNN features.

  Burak: I'm not saying what you did -- use CNN features to feed an
  online tracker. Yes, many people did such before. My worry is to
  make our paper look a christmas tree -- a paper w/ too many stuffs
  to evaluate under a certain theme. And, adding these new stuffs
  along the way of preparing any submissions continuously asks us to
  rewrite this paper from the top to all the way down. We need to
  focus on a certain idea when to submit a paper to a
  conference. Adding a bit more meats and stuffs to the main idea is
  usually done in a journal paper.

  If I add this to figure 5, it does not make sense, because all the
  trackers we compare, use hand-crafted features and run on CPU. For
  this reason, I wanted to compare EnKCF with deep features
  (higher-end system) and hand-crafted features (low-end system).

  Burak: Given what we agreed upon what you did, I think you can still
  put them together in that we're comparing different versions of
  apples, not orange, under the same criterion. Think about it.

  The figure 7(a) and figure 5 have almost the same range (0,73 and 0.70)
  I will update the figure 5 to have 0.73 range as well. I test the EnKCF
  with CNN features only on the UAV123 dataset.

  Burak: We don't expect the reviewers or readers to exactly see what
  we saw here. Keep their scales same -- whatever maximum value you
  choose for the y-axis for one graph, use the same scale to all other
  same graphs.}
\end{comment}
There have been many studies on applying a pretrained CNN features to
tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer features of the VGGNet
\cite{simonyan2014very} for this idea where their experiments showed
that the first convolutional layer features lead to slightly better
precision and success rates than the second
layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper
features. Their method employs the third convolutional layer features
to get the response map. In the next stage, they used the estimation
of the target's transition from the first stage to use the second
convolutional layer features. Finally, the first convolutional layer
features is extracted from the position estimated in the second
stage. This coarse-to-fine position estimation approach allows to
utilize more representative features of the object. However, such
approach requires multiple runs of a KCF at a single frame, increasing
the run-time complexity. For this reason, we follow a similar approach
to \cite{danelljan2015convolutional} to embed deep learning features.

Our {\it E}nKCF framework provides us with a flexibility to exploit different
level of abstractions in different KCFs. The translation filters,
$R_{t}^{L}$ and $R_{t}^{S}$, considers more than twice bigger area
than $R_{s}$. Taking this into account, we can assign deeper feature
encodings to $R_{s}$ as it requires less spatial information than
$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
the second layer features ($109\times109\times64$). This feature
assignment is represented as \textit{conv224-VGG} and shown in
fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
resolution at the first layers than than AlexNet
\cite{krizhevsky2012imagenet}.

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
results of utilizing DNN features. Two settings of utilizing the deep
features outperformed the HoG and color features as proposed in {\it
  E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in
success rates (AUC). The \textit{conv224-VGG} setting performed
slightly better than \textit{conv222-VGG} in precision while achieving
similar success rate (AUC).
